---
title: "Map"
author: "Valerie Chavez"
date: "2022-09-23"
output: html_document
---



Wish to explore differences in student experiences in HS across states

We have core survey items that measure different aspects of student/school experience, rigorously designed and tests for validity that measure:

Engagement: engage_fact
Academic Challenge: rigor_fact
Culture: climate_fact
Belonging & Peer Collaboration: peers_fact
Relationships: adult_fact
College & Career Readiness: prep_fact

Each survey item is compiled into a key factor or overall score. 




#libraries

```{r}
library(usmap)
library(ggplot2)
library(dplyr)
```


Prepping data 
```{r}
HSsegcount<-read.csv("/Users/valerier/Dropbox (CEP)/YouthTruth/Report Production/Reports_22JU/clients/comp_seg_22JU/OSE_HS/comp_seg_22JU/seg/segcount.csv")
HSsegmean<- read.csv("/Users/valerier/Dropbox (CEP)/YouthTruth/Report Production/Reports_22JU/clients/comp_seg_22JU/OSE_HS/comp_seg_22JU/seg/segmean.csv")

#removing variables other than state, and first column
HSsegcount<-HSsegcount[71:106,-1]
HSsegmean<-HSsegmean[71:106, -1]

```

```{r}
#renaming first column as state
names(HSsegcount)[names(HSsegcount) == 'val'] <- 'State'
names(HSsegmean)[names(HSsegmean) == 'val'] <- 'State'
```

```{r}
#Taking only state and factor variables

HSsegcount<-subset(HSsegcount, select= c("State", "engage_fact", "rigor_fact","climate_fact","peers_fact", "adult_fact", "prep_fact"))
HSsegmean<-subset(HSsegmean, select= c("State", "engage_fact", "rigor_fact","climate_fact","peers_fact", "adult_fact", "prep_fact"))
```

```{r}
region<- c("arkansas", "california", "colorado", "connecticut", "district of columbia", "florida", "georgia", "hawaii", "illinois", "indiana", "kansas", "louisiana", "massachusetts", "maryland", "maine", "michigan", "minnesota", "missouri", "mississippi", "north carolina", "new hampshire", "new jersey", "new mexico", "new york", "ohio", "oklahoma", "oregon", "pennsylvania", "rhode island","south carolina", "tennessee", "texas", "virginia", "vermont", "washington", "wisconsin")


HSsegmean<-cbind(region, HSsegmean)
HSsegcount<-cbind(region, HSsegcount)
```


```{r}
USmap<-map_data("state")
YTmap<-left_join(HSsegmean,USmap, by="region")
YTmapn<-left_join(HSsegcount,USmap, by="region")

```

```{r}
#"engage_fact", "rigor_fact","climate_fact","peers_fact", "adult_fact", "prep_fact"



ggplot(data=YTmap, mapping= aes(x = long, y = lat, group = group))+
  geom_polygon(color="white", aes(fill=prep_fact)) +
  theme_minimal()+
  #scale_colour_gradientn(colours = myPalette(100), limits=c(0, 1), )
  scale_fill_viridis_c(option = "plasma")+
    theme(axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        panel.background = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        panel.grid=element_blank())


  



```


